%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Diego}{Reyes}{ \urlstyle{same}\url{https://www.linkedin.com/in/diegofreyes/} \\
\href{mailto:dfreyes00@gmail.com}{dfreyes00@gmail.com} | 3057134513
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CERTIFICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certifications} 

\subsection{Java SE 8 Programmer}
\descript{Oracle Certified Associate}
\location{Aug 2016}
\sectionsep

\subsection{SOA Professional}
\descript{Arcitura Education Inc.}
\location{Mar 2018}
\sectionsep

\subsection{SOA Architect}
\descript{Arcitura Education Inc.}
\location{May 2018}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Universidad del Cauca}
\descript{Electronic and Telecommunications Engineering}
\location{May 2011 | Popayán, Cauca \\ Colombia}
\sectionsep

\subsection{Universidad del Cauca}
\descript{Network applications and services, specialization}
\location{May 2013 | Popayán, Cauca \\ Colombia}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LANGUAGES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Languages} 
Spanish: Native speaker \\
English: Working proficiency \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/diegof00}{\custombold{diegof00}} \\
LinkedIn://  \href{https://www.linkedin.com/in/diegofreyes/}{\custombold{diegofreyes}} \\
Blog:// \href{https://diegof00.github.io}{\custombold{diegof00}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Technical}
JEE \textbullet{} Spring \textbullet{} Maven \textbullet{} Gradle \\
Spring boot \textbullet{} SOAP \textbullet{} REST \\ 
microservices \textbullet{} docker \textbullet{} consul \\
serenity automation \textbullet{} TDD \textbullet{} BDD \\
SQL \textbullet{} Liquibase \textbullet{} flyway
Git \textbullet{} Linux  \\
\sectionsep

\location{Others:}
Javascript \textbullet{} AngularJS \textbullet{} Python3 \textbullet{} Flesk \\
Jekill \textbullet{} Jenkins pipelines \textbullet{} Groovy \\
\sectionsep

\subsection{Soft-skills}
Teamwork \textbullet{} Communication \textbullet{} Creative \\
Analytic \textbullet{} Problem Solving \textbullet{} Goals oriented  \\

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Blanc Labs}
\descript{| Software Engineer }
\location{Oct 2018 – Aug 20149| Bogotá, CO}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Exiger account - Java Microservices - Spring boot, consul, docker.
\item Equitable Bank account - Maintenance - Spring, Mule, AngularJS.
\end{tightemize}
\sectionsep

\runsubsection{Globant}
\descript{| Java Developer }
\location{Feb 2016 – Oct 2018 | Bogotá, CO}
\begin{tightemize}
\item Southwest Airlines account. People's Integrations Project. Java Developer and TAE, using gradle, serenity, selenium, JBehave, Spring, JAXWS. 
\item Southwest Airlines account. Vendor's Integrations Project. Java Developer and TAE, Spring integration, batch, quartz, oracle.  
\item Southwest Airlines account. Aircraft Parts Unit module. Java developer and TAE. Spring Integration, JMS, Tibco queues,ActiveMQ broker, Quartz.
\item Southwest Airlines account. Parts Transfer. Developer and TAE. Spring Web, Spring AOP, Gradle, Junit, JBehave, Selenium, Serenity BDD, WireMock, Oracle 11g, H2.
\item Southwest Airlines account. Fleet Planner Module. Developer and TAE. Spring Boot, AOP, Gradle, Oracle 11g, H2.\end{tightemize}
\sectionsep

\runsubsection{4Sight Technologies}
\descript{| Java Developer }
\location{Jun 2014 – Feb 2016 | Bogotá, CO}
\begin{tightemize}
\item Production support project for Mapfre USA. Maintenance TRONWEB application. Java JSE, PLSQL and Oracle database.
\item NewTron project for Mapfre USA. AngularJS, jade, node js, java 1.6, Spring 3.1, PLSQL, and Oracle.
.\end{tightemize}
\sectionsep

\runsubsection{Everis}
\descript{| Java Developer }
\location{Feb 2014 – Jun 2014 | Bogotá, CO}
\begin{tightemize}
\item Information system for Judicial Offices. JavaEE, JSF, Oracle.   
\end{tightemize}
\sectionsep

\runsubsection{Microshif SAS}
\descript{\href{http://microshif.com.co} | Java Freelance Developer }
\location{Aug 2013 – Dec 2013 | Bogotá, CO}
\begin{tightemize}
\item Ticket system  in JavaEE, JSF and firebirdDB.  
\end{tightemize}
\sectionsep

\runsubsection{Grupo ASD}
\descript{| Java Developer }
\location{Dec 2012 – Aug 2013 | Bogotá, CO}
\begin{tightemize}
\item Invima foods and medicaments registration. JavaEE, JSF, Oracle, PowerBuilder. 
\item Electoral software for National Elections. JavaSE, derbyDB, Java Swing. OCR. 
\end{tightemize}
\sectionsep

\runsubsection{Indra}
\descript{| Java Developer }
\location{Apr 2012 – Dec 2012 | Bogotá, CO}
\begin{tightemize}
\item Aviva account. Insurance application. Spring, Hibernate 1, Struts. 
\end{tightemize}
\sectionsep

\runsubsection{HDS - Health Digital Systems}
\descript{| Java Developer }
\location{Oct 2011 – Apr 2012 | Popayán, CO}
\begin{tightemize}
\item Aviva account. Insurance application. Spring, Hibernate, Struts. 
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Interest} 
\begin{tabular}{rll}
& Microservices architecture\\
& Machine Learning \\
& Blockchain \\
\end{tabular}
\sectionsep

\end{minipage} 
\end{document}
